\documentclass{tufte-handout}
\usepackage{privacytable}
\title{Privacy \& Security 101}

\author{Andy Zimolzak, Cryptoparty in Boston*\marginnote{* Remember to
    visit https://www.cryptoparty.in/boston to learn about future
    events! Usually we meet the last Wednesday of the month in
    Somerville.}}

\date{February 18, 2017}
\begin{document}

\maketitle

This topic is a \emph{process.} Nobody has to feel bad or depressed
about not being ``perfect.'' There is no finish line to cross and no
``one right answer'' to any question. Feel good that you moved in a
good direction \emph{today!} There are lots of details we can discuss
about any item.

\section{Who are you, and who is the threat?}

\noindent\hangindent=1em You're a ``regular person'' who doesn't want ad
companies to know all about you.

\noindent\hangindent=1em Regular person who has a stalker or
harasser.

\noindent\hangindent=1em Regular person who wants to avoid
identity theft.

\noindent\hangindent=1em Regular person who doesn't want malicious
software on your device.

\noindent\hangindent=1em You're a person with an opinion, and people are
trying to silence you or reveal sensitive information about you.


\section{Basic privacy/security tips}
Remember, you don't have to order one of everything on the menu! The
column ``Me?'' is about whether I personally use this tip all the time
(+++), some of the time$(\sim)$, or currently not at all (0).

\vspace{4ex}


\startlines

\tablesubsection Mobile\\
Set your phone to lock instantly. & +++ \\
Use ``Signal'' app for secure text messaging. & $\sim$ \\
Beware public wifi. & +++ \\
Look at which apps can track location in the background. & $\sim$ \\
Consider not using ``hey Siri,'' ``OK Google,'' and related. & +++ \\
Maybe don't even use Siri at all? & 0 \\
Consider switching off wifi \& Bluetooth on your phone until needed. & 0 \\
Is iPhone sharing your location? Messages app$\to$someone's name$\to$(i)
button & +++ \\


\tablesubsection Passwords\\
Don't repeat passwords. & $\sim$ \\
Use a really random password (or at least one without obvious
meaning). & $\sim$ \\
Two-factor authentication makes it harder to hack you. & $\sim$ \\
Think very hard before giving out any password. & +++ \\
Put some kind of password on most things that will take one (your home
wifi). & +++ \\

\stoplines

%\newpage
%%% page usually breaks here so far. Force it manually?

\startlines

\tablesubsection Web\\
Don't let the browser store your passwords. & $\sim$ \\
\emph{Consider} a non Chrome browser (at least not signed in). & $\sim$ \\
Use Tor browser: browse the Web nearly anonymously. & $\sim$ \\
Use non Google web search, e.g.\ DuckDuckGo. & $\sim$ \\
``Checkout as guest'' is at least one less account to worry about. &
$\sim$ \\
Set a Google alert on your name. & 0 \\
Sign out of Facebook etc.\ when you're done. & 0 \\
\qquad \small(however, staying signed in may be better than giving
browser your password) \\
Check your Facebook settings (``friends only''). & $\sim$ \\
If not using Tor, clear out history \& cookies every so often. & 0 \\

\tablesubsection Mail\\
Use a non GMail address. & $\sim$ \\
Click wisely (recognize tracking links or phishing,
mouse-over your links). & +++ \\
Set e-mail software to \emph{not} auto-download images. & $\sim$ \\
Don't give your email address to merchants etc.\ who ask. & $\sim$ \\


\tablesubsection Software/general\\
Enable auto updates. & $\sim$ \\
Use disk encryption. & $\sim$ \\
If it's critical and if you can, meet in person \& don't depend on
technology. & 0 \\
Pay in cash, especially for sensitive items. & $\sim$ \\
\stoplines


\section{The 99 most common passwords:}

If your password is on this list, \emph{change it right now!}
Warning: there is rude language in this list.

\begin{tabular}{lllllllll}

123456 & password & 12345678 & qwerty & 123456789 & 12345 & 1234 & 111111 & 1234567 \\
dragon & 123123 & baseball & abc123 & football & monkey & letmein & 696969 & shadow \\
master & 666666 & qwertyuiop & 123321 & mustang & 1234567890 & michael & 654321 & pussy \\
superman & 1qaz2wsx & 7777777 & fuckyou & 121212 & 000000 & qazwsx & 123qwe & killer \\
trustno1 & jordan & jennifer & zxcvbnm & asdfgh & hunter &  & buster & soccer \\
harley & batman & andrew & tigger & sunshine & iloveyou & fuckme & 2000 & charlie \\
robert & thomas & hockey & ranger & daniel & starwars & klaster & 112233 & george \\
asshole & computer & michelle & jessica & pepper & 1111 & zxcvbn & 555555 & 11111111 \\
131313 & freedom & 777777 & pass & fuck & maggie & 159753 & aaaaaa & ginger \\
princess & joshua & cheese & amanda & summer & love & ashley & 6969 & nicole \\
chelsea & biteme & matthew & access & yankees & 987654321 & dallas & austin & thunder \\
\end{tabular}

\end{document}

% LocalWords:  wifi Siri DuckDuckGo GMail lllllllll abc letmein qwertyuiop qaz
% LocalWords:  michael wsx fuckyou qazwsx qwe trustno jordan jennifer zxcvbnm
% LocalWords:  asdfgh harley andrew tigger iloveyou fuckme robert thomas daniel
% LocalWords:  starwars klaster george michelle jessica zxcvbn maggie aaaaaa
% LocalWords:  joshua amanda ashley nicole chelsea biteme matthew yankees
% LocalWords:  dallas austin
